Title

### 2024-08-30 paper.tex
remove garbage.  small wording fixes.

A basis for \(\spl_2\) is
\[e' := \begin{pmatrix}0 & 1 \\ 0 & 0 \\\end{pmatrix}, h' := \begin{pmatrix}1 & 0 \\0 & -1\end{pmatrix}, f' := \begin{pmatrix}0 & 0 \\1 & 0\end{pmatrix}.\]
Given a Lie algebra \(\mathfrak{g}\), and a homomorphism \(\phi : \spl_2 \to \mathfrak{g}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (TODO: what?)
If \(\mathfrak{g}\) is semisimple, then given any nilpotent \(e \in \mathfrak{g}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{g}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(\mathcal{S}_e := e + \ker \ad_f\).
By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{g}\), when \(\mathfrak{g}\) is semisimple.

@@

\begin{lemma}\label{big_centralizer}
    \[\mathfrak{z}_{\gl_{m + n}}(F) =  \left\{\begin{pNiceArray}{ccc|ccc}
        & & & & & \vert \\
        & X & & & & b    \\
        & & & & & \vert \\
       \hline
       \text{---} & a & \text{---} &  \\
        &  & &  & Y  \\
        & & & & & 
       \end{pNiceArray} : X \in \gl_m; Y \in \mathfrak{z}_{\gl_n}(f); a,b \in \mathbb{C}^m \right\}.\]
\end{lemma}
\begin{proof}
    Let \(Z = \begin{pmatrix}Z_{11} & Z_{12}\\Z_{21} & Z_{22}\end{pmatrix} \in \mathfrak{z}_{m + n}(F)\).
    We have 
    \[\begin{pmatrix}0 & Z_{12}f\\0 & Z_{22} f\end{pmatrix} =  ZF = FZ = \begin{pmatrix}0 & 0\\fZ_{21} & fZ_{22}\end{pmatrix}.\]
    We see that there is no restriction on \(Z_{11}\).
    The condition \(Z_{12}f = 0\) means that all but the last column of \(Z_{12}\) must be zero, and the condition \(0 = fZ_{21}\) means that all but the first row of \(Z_{21}\) must be zero.
    And the condition \(Z_{22}f = fZ_{22}\) means that \(Z_{22} \in \mathfrak{z}_{\gl_{m + n}}(f)\).
\end{proof}

@@

\subsection{A description of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
Recall that we have the map \(S \to \mathfrak{g}\) given by \(Z \mapsto (p(Z), Z)\), where \(p : \gl_{m + n} \to \gl_m\) is the coordinate projection.
We also have the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\).
From these two maps we define the fibered product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par To obtain an explicit description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we will begin by finding the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\).
As the image of the Springer resolution is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\) is simply \(S' = \{Z \in S : p(Z) \in \mathcal{N}_m, Z \in \mathcal{N}_{m + n}\}\).
\begin{lemma}
    \[S' = \left\{A_{X, a, b} := \begin{pNiceArray}{ccc|cccc}
    & & & & & & \vert \\
    & X & & & & & b    \\
    & & & & & & \vert \\
   \hline
   \text{---} & a & \text{---} & 0 \\
    & & & 1 & 0  & \\
    &  & & & \ddots & \ddots  \\
    & & & & & 1 & 0
   \end{pNiceArray} \in \mathcal{N}_{m + n}: a, b \in \mathbb{C}^m, X \in \mathcal{N}_m\right\}.\]
\end{lemma}
\begin{proof}
    As every element of \(\mathfrak{z}_{\gl_n}(f)\) is upper triangular, \cref{bottom_right_nilp} tells us that if a matrix of the form given in \cref{slodowy_slice} is nilpotent, and the upper-left block \(X\) is nilpotent as well, then \(e + Y\) must be nilpotent.
    Then, again using that every element \(Y \in \mathfrak{z}_{\gl_n}(f)\) is upper triangular, \cref{upper_triangle_zero} tells us that if \(e + Y\) is nilpotent, then \(Y = 0\).
    \par Hence every element of \(S'\) must simply have \(e\) in its bottom-right block.
    We see that every element of \(S'\) is of the desired form.
\end{proof}
This is not a fully explicit characterization of \(S'\), since we don't say which choices of \(X\) and \(a, b \in \mathbb{C}^m\) lead to \(A_{X, a, b}\) being nilpotent.
We could use \cref{block_determinant} to find a necessary and sufficient condition on \(X, a, b\); however, the description above of \(S'\) will be good enough for our purposes.
\begin{corollary}\label{sn_iso}
    \begin{align*}
        S \times_\mathfrak{g} \widetilde{\mathcal{N}} & = \\
        \{((X, A_{X, a, b}), ((X, A_{X, a, b}), \mathfrak{b})) : \mathfrak{b} \in \mathcal{B}, (X, A_{X, a, b}) \in \mathcal{N} \cap \mathfrak{b}\} & \cong \\
        \{(A_{X, a, b}, \mathfrak{b}) : \mathfrak{b} \in \mathcal{B}, (X, A_{X, a, b}) \in \mathfrak{b} \cap \mathcal{N}\} & .
    \end{align*}
\end{corollary}
We have a map \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) given by \((A_{X, a, b}, \mathfrak{b}) \mapsto X\).
We define the \emph{\(n\)-Slodowy-slice Springer fiber} at \(X \in \mathcal{N}_m\) to be the fiber \(\pi^{-1}(X)\).
Because \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\),  
\[\pi^{-1}(X) \cong \{(A_{X, a, b}, \mathfrak{b}_{m + n}) : A_{X, a, b} \in \mathfrak{b}_{m + n} \cap \mathcal{N}_{m + n}\} \times \{\mathfrak{b}_m : X \in \mathfrak{b}_m\}.\]
The right factor of the product is simply the usual Springer fiber at \(X\).
\par Let 
\[\mathcal{P}_X = \{(A_{X, a, b}, (V_i)) : \forall i. \; A_{X, a, b} V_i \subseteq V_{i - 1}\}.\]
Using our correspondence between Springer fibers in \(\mathcal{B}_{m + n}\) and flags of \(\mathbb{C}^{m + n}\), we see that \(\mathcal{P}_X\) is isomorphic to the left factor of \(\pi^{-1}(X)\).
In the next few sections, we will find the irreducible components of \(\mathcal{P}_X\).
Then we will use this, along with the result about the usual Springer fiber at \(X\), to find the irreducible components of \(\pi^{-1}(X)\) and then of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).

@@

\begin{lemma}\label{principal_bundle}
    The map \(\varphi\) is a principal \(G_{wr}\)-bundle.
    We need to show that \(G_{wr}\) acts freely and transitively on the fibers of \(\varphi\).
    It is obvious that \(G_{wr}\) acts freely on \(\mathcal{Q}_{wr} \times G\); it is enough to note that it acts freely on \(G\).
    \par Let \(y \in \mathcal{P}_{wr}\).
    By definition of \(\mathcal{P}_{wr}\), there is \(P_y \in G\) with \(P_y \cdot y \in \mathcal{Q}_{wr}\).
    We have
        \varphi^{-1}(y) = \{(x, P) : P \cdot x = y \} & = \\
        \{(P^{-1} y, P) : P^{-1} y \in \mathcal{Q}_{wr} \} & = \\
        \{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \cdot (P_y \cdot y) \in \mathcal{Q}_{wr}\} & .
    Using that \(G_{wr} = \{g \in G : g \cdot (P_y \cdot y) = P_y \cdot y\}\), the expression above becomes
    \[\{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \in G_{wr}\}.\]
    Setting \(Q := P^{-1} P_y^{-1}\), so that \(P = P_y^{-1} Q^{-1}\), the above becomes
        \{(Q \cdot (P_y \cdot y), P_y^{-1} Q^{-1}) : Q \in G_{wr}\} & = \\
        \{Q \cdot (P_y \cdot y, P_y^{-1}) : Q \in G_{wr}\} & .
        We see that the fibers are exactly the \(G_{wr}\)-orbits; or in other words, \(G_{wr}\) acts transitively on the fibers, as desired.
    % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.
    % Let \(X_1, ..., X_k\) be the irreducible components of \(\mathcal{Q}_{wr}\).
    % It is clear that \(V_{mr} = \bigcup_i \overline{\varphi(X_i \times G)}\).
    % And if we take \(x \in X_i \setminus \bigcup_{j \neq i} X_j\), it is clear (since \(G\) acts faithfully on itself) that \(\varphi(x, I_m)\)
    % All that remains is to show that \(X_i \notin \bigcup_{j \neq i} \overline{\varphi(X_i \times G)}\).
    % Indeed, 
Our strategy is to find the irreducible components \(X \subseteq \mathcal{Q}_{wr}\), and we will then argue that the irreducible components of \(\mathcal{P}_{wr}\) are of the form \(\varphi(X \times G)\).
So, we will now find the irreducible components of \(\mathcal{Q}_{wr}\).
\par Actually \(\mathcal{Q}_{wr}\) might be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
So, we will change basis to make \(r = 0\).
Let \(m' = m - r\), and \(n' = n + r\).
Let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
Let \(X' = J(\lambda)\).
(TODO: explain that \(A'\) is like \(A\), but with \(m',n'\) taking the place of \(m,n\).)
Let \(\mathcal{Q}' = \{(A'_{X', 0, b}, (V_i)) : \forall i. \; A_{X', 0, b} V_{i + 1} \subseteq V_i\}\).
\begin{lemma}\label{a_zero}
    \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\)
    Let \(e_{ij}'\) be the standard Jordan basis for \(X'\).
    Let \(f_1', ..., f_{n'}'\) be a basis for \(\mathbb{C}^n\), with \(A_{X', 0, b} f_{i + 1}' = f_i'\), and \(A_{X', 0, b} f_1 = (b, 0)\).
    Set \(m' := m - r\), and \(n' := n + r\).
    Define the linear map \(Q_{wr} : \mathbb{C}^{m' + n'} \to \mathbb{C}^{m + n}\) by:
        \item For all \(i\), \(e_{ij}' \mapsto e_{ij}\).
        \item For \(j = 1, ..., r\), \(f_{n + j}' \mapsto e_{w,(\lambda_w - r) + j}\).
        \item For \(j = 1, ..., n\), \(f_j' \mapsto f_j + e_{w, (\lambda_w - r) - n + j}\).
    % The inverse map \(Q_{wr}^{-1} : \mathbb{C}^{m + n} \to \mathbb{C}^{m' + n'}\) is
    % \begin{itemize}
    %     \item For all \(i \neq w\), \(e_{ij} \mapsto e_{ij}'\).
    %     \item For \(j = 1, ..., \lambda_w - r\), \(e_{wj} \mapsto e_{wj}'\).
    %     \item For \(j = 1, ..., r\), \(e_{wj} \mapsto f'_{n + j}\).
    %     \item For \(j = 1, ..., n\), \(f_j \mapsto f'_j - e_{w,\lambda_w - n + r}\)
    % \end{itemize}
    Change of basis by \(Q_{wr}\) maps \(\mathcal{Q}_{wr}\) to \(\mathcal{Q}'\), and conjugation by \(Q_{wr}^{-1}\) maps \(\mathcal{Q}'\) to \(\mathcal{Q}_{wr}\).
The next section finds the irreducible components of \(\mathcal{Q}'\).
To avoid death by primes, we will refer to it as \(\mathcal{Q}\), and refer to \(m',n'\) as \(m,n\), and so on, throughout the next section.

@@

\section{Future work}
The paper (TODO: cite) describes a bijection between the Steinberg variety (which is blah) and pairs of standard Young tableaux (each having shape blah).
The variety \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something like the Steinberg variety.
Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of standard Young tableaux: one having the shape of the Jordan form of \(X\), one having the shape of the Jordan form of \(A_{X, a, b}\).
\par Separately, this paper could use a nice introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).

>>>>

A basis for \(\spl_2\) is
\[e' := \begin{pmatrix}0 & 1 \\ 0 & 0 \\\end{pmatrix}, h' := \begin{pmatrix}1 & 0 \\0 & -1\end{pmatrix}, f' := \begin{pmatrix}0 & 0 \\1 & 0\end{pmatrix}.\]
Given a Lie algebra \(\mathfrak{g}\), and a homomorphism \(\phi : \spl_2 \to \mathfrak{g}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
% Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (TODO: what?)
If \(\mathfrak{g}\) is semisimple, then given any nilpotent \(e \in \mathfrak{g}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{g}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(\mathcal{S}_e := e + \ker \ad_f\).
By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{g}\), when \(\mathfrak{g}\) is semisimple.

@@

\begin{lemma}\label{big_centralizer}
    \[\mathfrak{z}_{\gl_{m + n}}(F) =  \left\{\begin{pNiceArray}{ccc|ccc}
        & & & & & \vert \\
        & X & & & & b    \\
        & & & & & \vert \\
       \hline
       \text{---} & a & \text{---} &  \\
        &  & &  & Y  \\
        & & & & & 
       \end{pNiceArray} : X \in \gl_m; Y \in \mathfrak{z}_{\gl_n}(f); a,b \in \mathbb{C}^m \right\}.\]
\end{lemma}
\begin{proof}
    Let \(Z = \begin{pmatrix}Z_{11} & Z_{12}\\Z_{21} & Z_{22}\end{pmatrix} \in \mathfrak{z}_{m + n}(F)\).
    We have 
    \[\begin{pmatrix}0 & Z_{12}f\\0 & Z_{22} f\end{pmatrix} =  ZF = FZ = \begin{pmatrix}0 & 0\\fZ_{21} & fZ_{22}\end{pmatrix}.\]
    There is no restriction on \(Z_{11}\).
    The condition \(Z_{12}f = 0\) means that all but the last column of \(Z_{12}\) must be zero, and the condition \(0 = fZ_{21}\) means that all but the first row of \(Z_{21}\) must be zero.
    And the condition \(Z_{22}f = fZ_{22}\) means that \(Z_{22} \in \mathfrak{z}_{\gl_{m + n}}(f)\).
\end{proof}

@@

\subsection{A description of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
Recall that we have the map \(S \to \mathfrak{g}\) given by \(Z \mapsto (p(Z), Z)\), where \(p : \gl_{m + n} \to \gl_m\) is the coordinate projection.
We also have the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\).
From these two maps we define the fibered product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par To obtain an explicit description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we will begin by finding the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\).
As the image of the Springer resolution is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\) is simply \(S' = \{Z \in S : p(Z) \in \mathcal{N}_m, Z \in \mathcal{N}_{m + n}\}\).
\begin{lemma}
    \[S' = \left\{A_{X, a, b} := \begin{pNiceArray}{ccc|cccc}
    & & & & & & \vert \\
    & X & & & & & b    \\
    & & & & & & \vert \\
   \hline
   \text{---} & a & \text{---} & 0 \\
    & & & 1 & 0  & \\
    &  & & & \ddots & \ddots  \\
    & & & & & 1 & 0
   \end{pNiceArray} \in \mathcal{N}_{m + n}: a, b \in \mathbb{C}^m, X \in \mathcal{N}_m\right\}.\]
\end{lemma}
\begin{proof}
    As every element of \(\mathfrak{z}_{\gl_n}(f)\) is upper triangular, \cref{bottom_right_nilp} tells us that if a matrix of the form given in \cref{slodowy_slice} is nilpotent, and the upper-left block \(X\) is nilpotent as well, then \(e + Y\) must be nilpotent.
    Then, again using that every element \(Y \in \mathfrak{z}_{\gl_n}(f)\) is upper triangular, \cref{upper_triangle_zero} tells us that if \(e + Y\) is nilpotent, then \(Y = 0\).
    \par Hence every element of \(S'\) must simply have \(e\) in its bottom-right block.
    So, every element of \(S'\) is of the desired form.
\end{proof}
This is not a fully explicit characterization of \(S'\), since we don't say which choices of \(X\) and \(a, b \in \mathbb{C}^m\) lead to \(A_{X, a, b}\) being nilpotent.
We could use \cref{block_determinant} to find a necessary and sufficient condition on \(X, a, b\); however, the description above of \(S'\) will be good enough for our purposes.
\begin{corollary}\label{sn_iso}
    \begin{align*}
        S \times_\mathfrak{g} \widetilde{\mathcal{N}} & = \\
        \{((X, A_{X, a, b}), ((X, A_{X, a, b}), \mathfrak{b})) : \mathfrak{b} \in \mathcal{B}, (X, A_{X, a, b}) \in \mathcal{N} \cap \mathfrak{b}\} & \cong \\
        \{(A_{X, a, b}, \mathfrak{b}) : \mathfrak{b} \in \mathcal{B}, (X, A_{X, a, b}) \in \mathfrak{b} \cap \mathcal{N}\} & .
    \end{align*}
\end{corollary}
We have a map \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) given by \((A_{X, a, b}, \mathfrak{b}) \mapsto X\).
We define the \emph{\(n\)-Slodowy-slice Springer fiber} at \(X \in \mathcal{N}_m\) to be the fiber \(\pi^{-1}(X)\).
Because \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\),  
\[\pi^{-1}(X) \cong \{(A_{X, a, b}, \mathfrak{b}_{m + n}) : A_{X, a, b} \in \mathfrak{b}_{m + n} \cap \mathcal{N}_{m + n}\} \times \{\mathfrak{b}_m : X \in \mathfrak{b}_m\}.\]
The right factor of the product is simply the usual Springer fiber at \(X\).
\par Let 
\[\mathcal{P}_X = \{(A_{X, a, b}, (V_i)) : \forall i. \; A_{X, a, b} V_i \subseteq V_{i - 1}\}.\]
Using our correspondence between Springer fibers in \(\mathcal{B}_{m + n}\) and flags of \(\mathbb{C}^{m + n}\), we see that \(\mathcal{P}_X\) is isomorphic to the left factor of \(\pi^{-1}(X)\).
In the next few sections, we will find the irreducible components of \(\mathcal{P}_X\).
Then we will use this, along with the result about the usual Springer fiber at \(X\), to find the irreducible components of \(\pi^{-1}(X)\) and then of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).

@@

\begin{lemma}\label{principal_bundle}
    The map \(\varphi\) is a principal \(G_{wr}\)-bundle.
\end{lemma}
\begin{proof}
    We need to show that \(G_{wr}\) acts freely and transitively on the fibers of \(\varphi\).
    It is obvious that \(G_{wr}\) acts freely on \(\mathcal{Q}_{wr} \times G\); it is enough to note that it acts freely on \(G\).
    \par Let \(y \in \mathcal{P}_{wr}\).
    By definition of \(\mathcal{P}_{wr}\), there is \(P_y \in G\) with \(P_y \cdot y \in \mathcal{Q}_{wr}\).
    We have
    \begin{align*}
        \varphi^{-1}(y) = \{(x, P) : P \cdot x = y \} & = \\
        \{(P^{-1} y, P) : P^{-1} y \in \mathcal{Q}_{wr} \} & = \\
        \{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \cdot (P_y \cdot y) \in \mathcal{Q}_{wr}\} & .
    \end{align*}
    Using that \(G_{wr} = \{g \in G : g \cdot (P_y \cdot y) = P_y \cdot y\}\), the expression above becomes
    \[\{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \in G_{wr}\}.\]
    Setting \(Q := P^{-1} P_y^{-1}\), so that \(P = P_y^{-1} Q^{-1}\), the above becomes
    \begin{align*}
        \{(Q \cdot (P_y \cdot y), P_y^{-1} Q^{-1}) : Q \in G_{wr}\} & = \\
        \{Q \cdot (P_y \cdot y, P_y^{-1}) : Q \in G_{wr}\} & .
    \end{align*}
    Thus the fibers are exactly the \(G_{wr}\)-orbits; or in other words, \(G_{wr}\) acts transitively on the fibers, as desired.
\end{proof}
Our strategy is to find the irreducible components \(X \subseteq \mathcal{Q}_{wr}\), and we will then argue that the irreducible components of \(\mathcal{P}_{wr}\) are of the form \(\varphi(X \times G)\).
So, we will now find the irreducible components of \(\mathcal{Q}_{wr}\).
\par Actually \(\mathcal{Q}_{wr}\) might be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
So, we will change basis to make \(r = 0\).
Let \(m' = m - r\), and \(n' = n + r\).
Let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
Let \(X' = J(\lambda)\).
(TODO: explain that \(A'\) is like \(A\), but with \(m',n'\) taking the place of \(m,n\).)
Let \(\mathcal{Q}' = \{(A'_{X', 0, b}, (V_i)) : \forall i. \; A_{X', 0, b} V_{i + 1} \subseteq V_i\}\).
\begin{lemma}\label{a_zero}
    \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\)
\end{lemma}
\begin{proof}
    Let \(e_{ij}'\) be the standard Jordan basis for \(X'\).
    Let \(f_1', ..., f_{n'}'\) be a basis for \(\mathbb{C}^n\), with \(A_{X', 0, b} f_{i + 1}' = f_i'\), and \(A_{X', 0, b} f_1 = (b, 0)\).
    Set \(m' := m - r\), and \(n' := n + r\).
    Define the linear map \(Q_{wr} : \mathbb{C}^{m' + n'} \to \mathbb{C}^{m + n}\) by:
    \begin{itemize}
        \item For all \(i\), \(e_{ij}' \mapsto e_{ij}\).
        \item For \(j = 1, ..., r\), \(f_{n + j}' \mapsto e_{w,(\lambda_w - r) + j}\).
        \item For \(j = 1, ..., n\), \(f_j' \mapsto f_j + e_{w, (\lambda_w - r) - n + j}\).
    \end{itemize}
    % The inverse map \(Q_{wr}^{-1} : \mathbb{C}^{m + n} \to \mathbb{C}^{m' + n'}\) is
    % \begin{itemize}
    %     \item For all \(i \neq w\), \(e_{ij} \mapsto e_{ij}'\).
    %     \item For \(j = 1, ..., \lambda_w - r\), \(e_{wj} \mapsto e_{wj}'\).
    %     \item For \(j = 1, ..., r\), \(e_{wj} \mapsto f'_{n + j}\).
    %     \item For \(j = 1, ..., n\), \(f_j \mapsto f'_j - e_{w,\lambda_w - n + r}\)
    % \end{itemize}
    Change of basis by \(Q_{wr}\) maps \(\mathcal{Q}_{wr}\) to \(\mathcal{Q}'\), and conjugation by \(Q_{wr}^{-1}\) maps \(\mathcal{Q}'\) to \(\mathcal{Q}_{wr}\).
\end{proof}
The next section finds the irreducible components of \(\mathcal{Q}'\).
To avoid death by primes, we will refer to it as \(\mathcal{Q}\), and refer to \(m',n'\) as \(m,n\), and so on, throughout the next section.

@@

\section{Future work}
The paper (TODO: cite) describes a bijection between the Steinberg variety (which is blah) and pairs of standard Young tableaux (each having shape blah).
The variety \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something like the Steinberg variety.
Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of standard Young tableaux: one having the shape of the Jordan form of \(X\), one having the shape of the Jordan form of \(A_{X, a, b}\).
\par Separately, this paper would benefit from an introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
